ISYE 6501

### 2022-09-07 hw2/submission.Rmd
correction ques 3.1

1.  Divide the data into 5 equal parts

@@

@@

```{r}
#Split org_data into 5 parts
df_copy = org_cc_data
df_copy$cross_validation_i <- sample(5, size = nrow(df_copy), replace = TRUE)

@@

### Question 3.1, Part 2: Train, Validation and Test on k-knn

#split data into 70% train, 15% validation and 15% test
df_copy2 = org_cc_data
df_copy2$split_i <- sample(100, size = nrow(df_copy), replace = TRUE)

df_copy2$split = "train"
df_copy2$split[70 < df_copy2$split_i] = "valid"
df_copy2$split[85 < df_copy2$split_i] = "test"

summary_df = aggregate(df_copy2$R1,list(df_copy2$split), 
          FUN = function(x) c(mean = mean(x), proportion = length(x)/nrow(df_copy2)))
print.data.frame(summary_df)
```

Again slight deviation from expected values is seen due to random effects

```{r}
df_train = df_copy2[df_copy2$split=="train",]
dim(df_train)
df_valid = df_copy2[df_copy2$split=="valid",]
dim(df_valid)
df_test= df_copy2[df_copy2$split=="test",]
dim(df_test)
```

@@

#### Run the above function for variety of k values

>>>>

0.  Divide the data into train,test (where test is final data used for evaluation)

1.  Divide the combined train and validation data into 5 equal parts

@@

### Step 0:

#split data into 70% train, 15% validation and 15% test
df_copy = org_cc_data
df_copy$split_i <- sample(100, size = nrow(df_copy), replace = TRUE)

df_copy$split = "train"
df_copy$split[70 < df_copy2$split_i] = "valid"
df_copy$split[85 < df_copy2$split_i] = "test"

summary_df = aggregate(df_copy,list(df_copy$split), 
          FUN = function(x) c(mean = mean(x), proportion = length(x)/nrow(df_copy)))
print.data.frame(summary_df)
```

```{r}
df_train = df_copy[df_copy$split=="train",]
dim(df_train)
df_valid = df_copy[df_copy$split=="valid",]
dim(df_valid)
df_test= df_copy[df_copy$split=="test",]
dim(df_test)
```

@@

```{r}
#Split the combined (train and validation) into 5 parts for CV
df_cv = rbind(df_train,df_valid)
dim(df_cv)
df_copy = df_cv
df_copy$cross_validation_i <- sample(5, size = nrow(df_copy), replace = TRUE)

@@

@@

```{r}
k_optimal = acc_df2[which.max(acc_df$mean_cv_accuracy),1]
acc_optimal_k = train_valid_func(df_train = df_copy, df_test = df_test, k_choice = k_optimal)
print (paste("With optimal k value, Accuracy on test =",acc_optimal_k))
```

The above accuracy is a true(or best) measure/evaluation for our model

### Question 3.1, Part 2: Train, Validation and Test

#### Run the train valid func function for variety of k values
